---
output:
  html_document:
    keep_md: yes
---
# My Assignment

## Loading and preprocessing the data

```{r}
library(ggplot2)
setwd("c:\\users\\user\\desktop")
data = read.csv("activity.csv")
data$interval = (data$interval %% 100) / 60 + as.integer(data$interval / 100)
```

## What is mean total number of steps taken per day?

Total number of steps taken per day.

```{r}
stepPerDay = xtabs(steps ~ date, data = data)
print(as.data.frame(stepPerDay))
```

A histogram of the total number of steps taken each day.

```{r}
barplot(names.arg = names(stepPerDay), stepPerDay, xlab = "Intervals", ylab = "Steps")
```


The mean and median of the total number of steps taken per day.

```{r}
summary(as.vector(stepPerDay))[c("Mean", "Median")]
```

## What is the average daily activity pattern?

A time series plot.

```{r}
freqPerInt = xtabs(steps ~ interval, data = data)
freqPerInt = freqPerInt / xtabs(!is.na(steps) ~ interval, data = data)
freqPerInt = as.data.frame(freqPerInt)
ggplot(freqPerInt, aes(x = as.numeric(as.character(interval)), y = Freq)) +
  geom_line() +
  xlab("Interval") + ylab("Steps") +
  xlim(0,24) + ylim(0, NA)
```

Which interval contains the maximun number of step.

```{r}
as.character(freqPerInt$interval[which.max(freqPerInt$Freq)])
```

## Imputing missing values

Summery of NAs in the data set.

```{r}
table(!complete.cases(data))
```

Fill in the NAs.

```{r}
for(i in 1:dim(data)[1])
  if(is.na(data$steps[i]))
  {
    if(!is.na(freqPerInt$Freq[data$interval[i] / 5 + 1]))
      data$steps[i] = freqPerInt$Freq[data$interval[i] / 5 + 1]
    else
      data$steps[i] = stepPerDay[names(stepPerDay) == data$date[i]][1]
  }
```

Make a histogram of the total number of steps taken each day.

```{r}
stepPerDay = xtabs(steps ~ date, data = data)
barplot(stepPerDay)
```

Mean and median total number of steps taken per day.

```{r}
summary(as.vector(stepPerDay))[c("Median", "Mean")]
```

## Are there differences in activity patterns between weekdays and weekends?

Create a new factor variable in data frame.

```{r}
data$weekday = factor(weekdays(as.Date(as.character(data$date))) %in% c("ÐÇÆÚÁù","ÐÇÆÚÈÕ"), levels = c(TRUE, FALSE), labels = c("weekend", "weekday"))
freqPerInt2 = as.data.frame(xtabs(steps ~ interval + weekday, data = data))
```

Creat final plot.

```{r}
ggplot(freqPerInt2, aes(x = as.numeric(as.character(interval)), y = Freq)) +
  geom_line() +  facet_grid(weekday ~ .) + 
  xlab("Interval")+ ylab("steps") +
  xlim(0,24) + ylim(0, NA)
```